Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/model.tex

\asedit{\xhdr{Consistency.}}
While we experiment with various MAB instances and parameter settings, in the main paper we only report plots for selected, representative experiments. Additional plots will be published in the full version. Unless noted otherwise, our findings are based on and consistent with all these plots.

>>>>

\xhdr{Consistency.}
While we experiment with various MAB instances and parameter settings, we only report on selected, representative experiments in the body of the paper. Additional plots and tables are provided in the appendix. Unless noted otherwise, our findings are based on and consistent with all these experiments.

### 2019-02-14 paper/content/non_greedy_choice.tex

However, it takes a significant amount of randomness and a relatively large time horizon for this convergence to occur. Even with $T = 10000$ and $\epsilon = 0.1$ we see that \DEG still outperforms \DG on the Heavy-Tail MAB instance as well as that \TS only starts to become weakly dominant at $T = 10000$ for the Uniform MAB instance. Table \ref{tab:non_greedy_table} also shows that another difference between the two choice models is that \HMR leads to lower variance in market shares across simulations compared to HardMax.

>>>>

However, it takes a significant amount of randomness and a relatively large time horizon for this convergence to occur. Even with $T = 10000$ and $\epsilon = 0.1$ we see that \DEG still outperforms \DG on the Heavy-Tail MAB instance as well as that \TS only starts to become weakly dominant at $T = 10000$ for the Uniform MAB instance. Table \ref{tab:non_greedy_table} also shows that another difference between the two choice models is that \HMR leads to lower variance in market shares across simulations compared to \HM.
